Making Sequential Programs Deterministic

### 2019-04-06 design.tex
typesetting rule

We annotated the \codeid{equals()} method of the \<Set> class in the JDK as
\begin{verbatim}
PolyDet("up") boolean equals(PolyDet Set<E> this, PolyDet Object o)
\end{verbatim}
While this is sound, it is imprecise in the case of \codeid{OrderNonDet
  Set}s.\todo{Explain why.}
 We added the rule shown in \cref{fig-precision-rules} to our checker to improve precision.
\begin{figure}
    \todo{add line break}
    $\infer[\rulename{set precision}]{\Gamma \vdash \|x.equals(y)| : \<Det> \ \|boolean|}{\Gamma \vdash \|x| : \<OrderNonDet> \ \|Set|\angles{ \kappa_{x} \ \beta_{x}}, \|y| : \<OrderNonDet> \ \|Set|\angles{ \kappa_{y} \ \beta_{y}} & \kappa_{x} \ \beta_{x} \nsqsubseteq \<OrderNonDet> \ \<List> & \kappa_{y} \ \beta_{y} \nsqsubseteq \<OrderNonDet> \ \<List> }$

>>>>

We annotated the \codeid{equals()} method of the \<Set> class in the JDK as
\begin{verbatim}
PolyDet("up") boolean equals(PolyDet Set<E> this, PolyDet Object o)
\end{verbatim}
While this is sound, it is imprecise in the case of \codeid{OrderNonDet
  Set}s.\todo{Explain why.}
 We added the rule shown in \cref{fig-precision-rules} to our checker to improve precision.
\begin{figure}
    \begin{align*}
    \infer[\rulename{set precision}]{\Gamma \vdash \|x.equals(y)| : \<Det> \ \|boolean|}
    {
        &\Gamma \vdash \|x| : \<OrderNonDet> \ \|Set|\angles{ \kappa_{x} \ \beta_{x}}, \|y| : \<OrderNonDet> \ \|Set|\angles{ \kappa_{y} \ \beta_{y}} \\
        & \kappa_{x} \ \beta_{x} \nsqsubseteq \<OrderNonDet> \ \<List>        \hspace{150pt}   \\
        & \kappa_{y} \ \beta_{y} \nsqsubseteq \<OrderNonDet> \ \<List>     \hspace{150pt}    
    }
    \end{align*}
    \bigskip
